Summer 2024 Report

### 2024-10-23 Relations/Report.tex
wf-stuff
Updated WF graph

\newcommand{\tto}{\twoheadrightarrow}
\newcommand{\sse}{\subseteq}
\newcommand{\bset}{\mathbf{Set}}

@@

    % Arrows
    \draw[->, thick, darkgreen] (std1) -- (dn1);
    \draw[->, thick, darkgreen] (dn1) -- (weak1);
    \draw[<->, thick, darkgreen] (std1) -- (std2);
    \draw[->, thick, darkgreen] (std2) -- (dn2);
    \draw[->, thick, darkgreen] (dn2) -- (weak2);
    \draw[<->, thick, darkgreen] (weak1) -- (weak2);
    \draw[->, thick, red] (std2) -- (std3) node[pos=0.5, right, red] {?};
    \draw[->, thick, darkgreen] (std3) -- (dn3);
    \draw[->, thick, darkgreen] (dn3) -- (weak3);
    \draw[->, thick, darkgreen] (weak2) -- (weak3);
    \draw[->, thick, darkgreen, bend left] (std3) to (std4);
    \draw[->, thick, darkgreen, bend left] (weak3) to (weak4);
    \draw[->, thick, darkgreen] (std4) -- (dn4);
    \draw[->, thick, darkgreen] (dn4) -- (weak4);
    \draw[->, thick, red, bend left] (std4) -- (std3) node[pos=0.5, left, red] {?};
    \draw[->, thick, red, bend left] (weak4) -- (weak3) node[pos=0.5, left, red] {?};
  \end{tikzpicture}
\end{center}

@@

>>>>

\newcommand{\tto}{\twoheadrightarrow}
\newcommand{\sse}{\subseteq}
\newcommand{\bset}{\mathbf{Set}}
\newcommand{\nat}{\mathbb{N}}

@@

    % Arrows
    \draw[->, thick, darkgreen] (std1) -- (dn1);
    \draw[->, thick, darkgreen] (std1.west) to[out=180, in=90, bend right] (std4);
    \draw[->, thick, darkgreen] (dn1) -- (weak1);
    \draw[<->, thick, darkgreen] (std1) -- (std2);
    \draw[->, thick, darkgreen] (std2) -- (dn2);
    \draw[->, thick, darkgreen] (dn2) -- (weak2);
    \draw[<->, thick, darkgreen] (weak1) -- (weak2);
    \draw[->, thick, red] (std2) -- (std3) node[pos=0.5, right, red] {?};
    \draw[->, thick, darkgreen] (std3) -- (dn3);
    \draw[->, thick, darkgreen] (dn3) -- (weak3);
    \draw[->, thick, darkgreen] (weak2) -- (weak3);
    \draw[->, thick, darkgreen, bend left] (std3) to (std4);
    \draw[->, thick, darkgreen, bend left] (weak3) to (weak4);
    \draw[->, thick, darkgreen] (std4) -- (dn4);
    \draw[->, thick, darkgreen] (dn4) -- (weak4);
    \draw[->, thick, red, bend left] (std4) -- (std3) node[pos=0.5, left, red] {?};
    \draw[->, thick, red, bend left] (weak4) -- (weak3) node[pos=0.5, left, red] {?};
  \end{tikzpicture}
\end{center}

@@

\section{Classical Principles}
Principles we are considering
\begin{itemize}
  \item Decidability of equality on $A$
  \item Decidability of the relation $R$
  \item When relevant, decidability of the given precicate $P$
  \item Not-not-closure of being accessible
  \item Not-not-closure of $R$
  \item Not-not-closure of $P$
  \item Decidability of whether a given element is an $R$-normal form
  \item When relevant, local/element-wise versions of the above
  \item Markov's principle:
  \begin{itemize}
    \item In $wfMin_0 \to wfSeq$.

    Given a sequence $s : \nat \to A$, let $E(a) = \exists n \in \nat. s n \equiv a$.

    Need: $\forall a. \lnot\lnot E(a) \to E(a)$, i.e.,
    \[\lnot\lnot \big(\exists n \in \nat. s n \equiv a\big)
          \to \big(\exists n \in \nat. s n \equiv a\big)\]

  \end{itemize}
\end{itemize}
